Streaming CityJSON datasets

### 2024-04-26 paper/main.tex
Some fixes

We have processed all the datasets from Table~\ref{tab:datasets} with two simple Python scripts that iterate through the city objects and their geometries, and increment a global counter for the geometry type (\texttt{Solid} or \texttt{MultiSurface}) and report it at the end.
This is just an example of a simple local operation, any other operation such as calculating the area of the façades or counting the number of windows could have been performed.
The results for both the maximum memory footprint\footnote{The resident set size (RSS) was used, which is the portion of main memory occupied by the Python script} and the time used are shown in Table~\ref{tab:ramtime}.
The scripts are available at \url{https://github.com/cityjson/paper_cjseq/tree/main/scripts/}.
\begin{table*}
  \centering
  \caption{Comparison of the processing time and max RAM use for processing the same data stored in a CityJSON file and a CityJSONSeq file.}
  \small
  \begin{tabular}
    {@{}lcrrcrrr@{}}\toprule
    &&  \multicolumn{2}{c}{\textbf{RAM used (MB)}} && \multicolumn{3}{c}{\textbf{time (s)}} \\ 
    \cmidrule{3-4} \cmidrule{6-8} 
     && CityJSON & CityJSONSeq && CityJSON & CityJSONSeq & diff \\
    \midrule
     \textbf{3DBAG}         &&   76.9 &  16.1  &&   0.10 & 0.07 & 1.4X \\
     \textbf{3DBV}          && 4101.8 & 123.8  &&  10.95 & 3.59 & 3.1X \\
     \textbf{Helsinki}      && 3743.1 &  15.0  &&  13.39 & 2.74 & 4.9X \\
     \textbf{Helsinki\_tex} && 5004.8 &  19.1  &&  29.60 & 4.72 & 6.3X \\
     \textbf{Ingolstadt}    &&   65.5 &  21.3  &&   0.08 & 0.06 & 1.3X \\
     \textbf{Montréal}      &&   79.3 &  20.8  &&   0.11 & 0.07 & 1.6X \\
     \textbf{NYC}           &&  949.5 &  16.0  &&   1.78 & 0.70 & 2.5X \\
     \textbf{Railway}       &&   69.6 &  29.6  &&   0.09 & 0.07 & 1.3X \\
     \textbf{Rotterdam}     &&   42.4 &  14.6  &&   0.04 & 0.04 & 1.0X \\
     \textbf{Vienna}        &&   60.1 &  15.7  &&   0.06 & 0.05 & 1.2X \\
     \textbf{Zurich}        && 2793.1 &  16.3  &&   6.05 & 2.00 & 3.0X \\
    \bottomrule
  \end{tabular}%
  \label{tab:ramtime}
\end{table*}

The results indicate that there is a very significant benefit to using CityJSONSeq over CityJSON, at least for operations that do not require analysing or processing city objects that are close to each other.
Operations like calculating volumes, merging and subsetting files, finding city objects with specific attributes, etc.\ will all use significantly less memory and will be significantly faster.

>>>>

We have processed all the datasets from Table~\ref{tab:datasets} with two simple Python scripts that iterate through the city objects and their geometries, and increment a global counter for the geometry type (\texttt{Solid} or \texttt{MultiSurface}) and report it at the end.
This is just an example of a simple local operation, any other operation such as calculating the area of the façades or counting the number of windows could have been performed.
The results for both the maximum memory footprint\footnote{The resident set size (RSS) was used, which is the portion of main memory occupied by the Python script} and the time used are shown in Table~\ref{tab:ramtime}.
The scripts are available at \url{https://github.com/cityjson/paper_cjseq/tree/main/scripts/}.
\begin{table*}
  \centering
  \caption{Comparison of the processing time and maximum RAM use for processing CityJSON and CityJSONSeq files.}
  \small
  \begin{tabular}
    {@{}lcrrcrrr@{}}\toprule
    &&  \multicolumn{2}{c}{\textbf{RAM used (MB)}} && \multicolumn{3}{c}{\textbf{time (s)}} \\ 
    \cmidrule{3-4} \cmidrule{6-8} 
     && CityJSON & CityJSONSeq && CityJSON & CityJSONSeq & diff \\
    \midrule
     \textbf{3DBAG}         &&   76.9 &  16.1  &&   0.10 & 0.07 & 1.4X \\
     \textbf{3DBV}          && 4101.8 & 123.8  &&  10.95 & 3.59 & 3.1X \\
     \textbf{Helsinki}      && 3743.1 &  15.0  &&  13.39 & 2.74 & 4.9X \\
     \textbf{Helsinki\_tex} && 5004.8 &  19.1  &&  29.60 & 4.72 & 6.3X \\
     \textbf{Ingolstadt}    &&   65.5 &  21.3  &&   0.08 & 0.06 & 1.3X \\
     \textbf{Montréal}      &&   79.3 &  20.8  &&   0.11 & 0.07 & 1.6X \\
     \textbf{NYC}           &&  949.5 &  16.0  &&   1.78 & 0.70 & 2.5X \\
     \textbf{Railway}       &&   69.6 &  29.6  &&   0.09 & 0.07 & 1.3X \\
     \textbf{Rotterdam}     &&   42.4 &  14.6  &&   0.04 & 0.04 & 1.0X \\
     \textbf{Vienna}        &&   60.1 &  15.7  &&   0.06 & 0.05 & 1.2X \\
     \textbf{Zurich}        && 2793.1 &  16.3  &&   6.05 & 2.00 & 3.0X \\
    \bottomrule
  \end{tabular}%
  \label{tab:ramtime}
\end{table*}

Notice that the dataset \textbf{3DBV} contains the ground that has been triangulated, and a few large areas are stored as \texttt{LandUse} and contain several triangles, this is the reason why the maximum memory use is larger than for other datasets.

The results in Table~\ref{tab:ramtime} indicate that there is a very significant benefit to using CityJSONSeq over CityJSON, at least for operations that do not require analysing or processing city objects that are close to each other.
Operations like calculating volumes, merging and subsetting files, finding city objects with specific attributes, etc.\ will all use significantly less memory and will be significantly faster.
